---
title: "Collect-actual-Concepts"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Collect-actual-Concepts-From-Cs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
## Problem
Preparing end sets is an extremely important stage of working with OMOP СDM. A specialist has many functions in his arsenal that allow him to optimize the process: descendants, relationships, exclusions, etc.
However, it happens when these functions are not available at the analysis level, which requires the specialist to create a set of concepts from the concept set in order to use all the records explicitly

## Recipie 
Collect all concept ids from concept set Capr

## Cooking
```{r setup}
library(tidyOhdsiRecipies)
library(dplyr)
library(Capr)
rlang::check_installed("Eunomia")
```


##### Load mock data
```{r}
con <- suppressMessages(DatabaseConnector::connect(Eunomia::getEunomiaConnectionDetails()))
## Create Capr concept set with ingredient
diclofenac <- cs(descendants(1124300), name = "diclofenac")
```

```{r}
all_diclofenac <- listConceptIdsFromCs(diclofenac, con, vocabularyDatabaseSchema = "main")
DatabaseConnector::disconnect(con)
all_diclofenac$diclofenac
```

#### Conclusion
Not to good result due to lack of real descendants, but using more sufficient data you will get all the concept_ids from concept set expression
