---
title: "Create many concept-based cohorts"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Create many concept-based cohorts}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
## Problem
The need to create many cohorts based on a concept set/sets with simple attributes, for example, observation before the index, or special ways to exit a cohort. If you are familiar with the `Capr` package, then of course you can use it, but if your concept set contains source concepts that you would like to use, `Capr` does not allow this

## Recipie 
Collect the necessary concept sets, set up exit criteria and get cohorts

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Cooking
Load required packages
```{r setup}
library(tidyOhdsiRecipies)
library(tidyverse)
```
#### For this puprose we will use PHN.json cohort located in inst/cohorts directory

```{r}
## read the cohort and get list from json
cohortDonor <- jsonlite::read_json(fs::path(fs::path_package("tidyOhdsiRecipies"), "cohorts", "PHN.json"))
caprConceptSets <- collectCaprCsFromCohort(cohortDonor)
print(caprConceptSets$hiv)
```

As a result we got names list of concept sets from cohort donor

```{r}
namesOfCs <- names(caprConceptSets)
print(namesOfCs)
```


```{r}
cohorts <- purrr::map(
  caprConceptSets,
  ~ tidyOhdsiRecipies::createCaprConceptSetCohort(
    conceptSet = .x,
    limit = "all",
    requiredObservation = c(1, 1),
    end = "fixed_exit",
    endArgs = list(
        index = c("startDate"), 
        offsetDays = 1
    ),
    addSourceCriteria = FALSE
  )
)
names(cohorts)
```
```{r}
cohortsToCreate <- createCohortsToCreate(
  cohorts = cohorts
)
head(cohortsToCreate)
```


Or Darwin `CDMConnector` CohortSet

```{r}
CohortSet <- CirceR2CDMConn(cohorts)
head(CohortSet)
```
